---
title: "An alternative 2d histogram visualisation"
output: html_notebook
---

```{r setup, echo=FALSE}
opts_chunk$set(echo = TRUE, cache=FALSE)
read_chunk('locs_to_image.R')
```

I had a slight problem in one of my [previous notes](https://bobturneruk.github.io/Visualising_LM_data.nb.html) that I basically ignored! One of my image plots had some spurious transparent lines running accross it.

My original code did this to load the dataset:

```{r load_localisations}
Tubulins_I<-read.csv("https://bobturneruk.github.io/Tubulins_I.csv")
```

Then this for the plot (50 nm pixel size):

```{r plot_localisations, fig.width=10, fig.height=10}
library(ggplot2)
ggplot(Tubulins_I, aes(x=Tubulins_I$x..nm., y=Tubulins_I$y..nm.))+
  geom_bin2d(binwidth=50, drop = FALSE)+
  coord_fixed()
```

Notice the two transparent lines at the top of the plot. This is not entirely what I wanted. A bit of googling revealed that this has been [logged as an issue, but it is not actually a bug](https://github.com/tidyverse/ggplot2/issues/2202). I have therefore written (but not extensively tested!) a little utility function that uses the **raster** library to generate, in effect, a 2d histogram as a data frame which can then be plotted using **ggplot2**, so I can keep using all of the other good stuff in **ggplot2** with my localisation data.

```{r locs_to_image}
```


I can then use this function to get a data frame which I can visualise using **geom_tile**.

```{r replot_localisations, fig.width=10, fig.height=10}

image_df<-locs_to_image(Tubulins_I$x..nm.,Tubulins_I$y..nm.,50)

ggplot(image_df,aes(x=x_nm,y=y_nm))+
  geom_tile(aes(fill=count))+
  coord_fixed()

```

And no transparent lines.

See my [website](https://sites.google.com/view/robert-turner) for more examples. Contact me on bob dot turner dot uk at gmail dot com with comments or questions.

