---
title: "Shiny Cluster Sim"
author: "Bob Turner"
date: "11 January 2018"
output: html_document
runtime: shiny
---

This App lets you simulate clustered single molecule localisation microscopy (PALM/STORM/etc.) data and then use the [DBSCAN algorithm](https://en.wikipedia.org/wiki/DBSCAN) (an unsupervised machine learning approach) to try and figure which molecule should be in what cluster. The first four sliders control the simulation. Cluster locations are drawn at random from a uniform distribution in a **500x500 nm square**. The clusters thenselves are also square and molecules are randomly distributed within them, again from a uniform distribution. **Uncertainty in localisation** is simulated by adding offsets to each molecule location randomly drawn from a normal distribution. Any points outside the 500x500 nm square after all this are deleted.

You might image we're looking at **lipid rafts**, or **multi-protein complexes**.

The final two sliders control the DBSCAN algorithm. **Eplison** is the maximum spacing between two molecules for them to be considered part of the same cluster. **Minimum points** is the smallest number of molecules required to form a cluster.

```{r clustersim, echo=FALSE}

source('locs_to_image.R')
source('simulator.R')

inputPanel(

  sliderInput("n_clusters", label = "Number of clusters:",
              min = 1, max = 50, value = 20, step = 1),

  sliderInput("n_per_cluster", label = "Molecules per cluster:",
              min = 1, max = 200, value = 20, step = 1),
 
  sliderInput("cluster_dim", label = "Cluster dimensions (nm):",
              min = 1, max = 200, value = 15, step = 1),

  sliderInput("loc_p", label = "Localisation precision (variance, nm):",
              min = 1, max = 50, value = 15, step = 1),
  
  sliderInput("epsilon", label = "DBSCAN epsilon:",
              min = 1, max = 50, value = 20, step = 1),
  
  sliderInput("min_pts", label = "DBSCAN minimum points:",
              min = 1, max = 10, value = 3, step = 1)
  
)
```

```{r render, echo=FALSE}

renderPlot({
  
  library(magrittr)
  
  set.seed(1)
  
  my_sim<-simulate_uniform(n = input$n_clusters, xy_image = 500) %>%
    create_clusters(molecules_per_cluster = input$n_per_cluster, cluster_size = input$cluster_dim) %>%
    create_error(precision = sqrt(input$loc_p)) %>%
    crop(image_xy = 500)
  
  library(ggplot2)

  image_df<-locs_to_image(my_sim$x,my_sim$y,5)
  
  image<-ggplot(image_df,aes(x=x_nm,y=y_nm))+
          geom_tile(aes(fill=count))+
          coord_fixed()+
          ggtitle("Image as histogram")
  
  library(fpc)
  
  my_sim$cluster<-dbscan(my_sim, eps = input$epsilon, MinPts = input$min_pts)$cluster
  
  scatter<-ggplot(my_sim,aes(x=x,y=y,colour=cluster))+
          geom_point(alpha=0.4)+
          coord_fixed()+
          scale_colour_distiller(palette="Accent")+
          ggtitle(paste(max(my_sim$cluster),"clusters found"))
  
  library(gridExtra)
  library(grid)
  
  grid.arrange(image,scatter, ncol=2)
  
})
```

You will notice that if there are a small number of clusters and they are a long way apart, this method works well. If there are lots of relatively large clusters, it starts to break down.

Source at https://github.com/bobturneruk/rSMLMClusters.

See my [website](https://sites.google.com/view/robert-turner) for more examples. Contact me on bob dot turner dot uk at gmail dot com with comments or questions.

